New Insights on the Role of Context in the Perception of a Human-like Robot

### 2015-04-09 main.tex
Update on Overleaf.

To study this effect, we propose an original methodology based on eye-tracking
and a serie of stimuli that are visually identical and yet elicit different
assumptions regarding the cognitive capabilities of the robot. We then correlate
the gaze patterns with established questionnaires that assess anthropomorphic
attributions.

@@

Anthropomorphism is seen as a special kind of social (human-like) engagement
with robots. We made an attempt to analyze anthropomorphism in a
\textit{human-robot} interaction by utilizing the gaze patterns of the
participants (who watched this interaction). These gaze patterns were compared
to the gaze patterns for a similar \textit{human-human} interaction setting. The
``human'' part of the human-robot and human-human interactions mentioned above
is only in the form of an audio command and not physically present in the scene.
Hence, we represent the interactions with $\mathcal{R}$ and $\mathcal{H}$ in
this report for the human-robot and human-human settings respectively.

There were four hypotheses made in this experiment. We hypothesized
(\textbf{H1}) that the gaze patterns can distinguish between $\mathcal{H}$ and
$\mathcal{R}$ interaction scenarios. Further, this gaze pattern difference can
be denoted as the distribution of gaze on areas of interest in the scene.
Secondly, we hypothesized (\textbf{H2}) that the difference in gaze patterns
between $\mathcal{H}$ and $\mathcal{R}$ conditions
($\delta_{\mathcal{H},\mathcal{R}}$) correlate with the participants'
\textit{initial capital of anthropomorphism} (ICA), where the ICA was measured
as the sum of the ratings (responses) given by the participants to the questions
of the pre-questionnaire. This means that for participants whose ICA is low, the
gaze patterns should be significantly different for the $\mathcal{R}$ as
compared to that for the $\mathcal{H}$ videos and vice-versa.

@@

We used stationary eye tracking technique for tracking the gaze patterns and
``Nao", a robot manufactured by Aldebaran Robotics was used in this
experiment. We prepared the scripts for the robot using Choreographe. The
interactions were recorded as videos and were then shown to the participants.
The scenarios that were covered in the videos were aimed at eliciting the
human-like or high-cognitive (HC) feelings for the robot in one setting and
robot-like or low-cognitive (LC) feelings in the other setting. For example, we
had a scene, where the robot is asked by the human to \textit{``pick up the
brown toy"} and in another scene, with the same video, the robot is asked to
\textit{``pick up its favorite toy"}. We tried to keep our distribution of
participants uniform across all variations of the scenarios to avoid any biases
to our results. The change in the feelings of participants were recorded in the
form of response to two questionnaires before and after the experiment. The
difference in the response of the two questionnaires was used to measure the
impact the videos had on the participants.

As mentioned earlier, the human element in the $\mathcal{R}$ interaction was in
the form of only a human voice, basically a command given by the human to the
robot. This command (\eg ``pick up the brown toy") was used to prime
the context thereby classifying the scenario as LC or HC. Initially we had three
different scenarios where the robot/human was asked:

@@

After filling the pre-questionnaire, participants watched the $\mathcal{R}$ and
$\mathcal{H}$ interaction videos.

@@

Among the 10 AOIs, we grouped the AOIs corresponding to the actor into 4
categories : Head, Arm (containing both arms and hands), Torso, Leg(containing
both legs). And this is the result that we obtained from the ANOVA between gaze
patterns on the AOIs versus the $\mathcal{H}$ and $\mathcal{R}$ conditions :

\textit{\textbf{head}}: the fixations on the head for the $\mathcal{H}$ scene
were observed to more than that for the $\mathcal{R}$ scene (F[1,36] = \ 6.60, p
< .05)

\textit{\textbf{arm}}\ : the fixations on the arms for the $\mathcal{H}$ scene
were also greater than that for the $\mathcal{R}$ scene (F[1,36] = 18.65, p <
.01)

\textit{\textbf{leg}}\hspace{0.18cm} : the fixations on the legs were much lower
for the $\mathcal{H}$ scene as compared to the $\mathcal{R}$ scene (F[1,36] = \
2.89, p < .1)

\textit{\textbf{torso}} : the fixations on the torso was more for the
$\mathcal{H}$ scene than for the $\mathcal{R}$ scene (F[1,36] = \ 3.54, p < .1)

@@

This test was done only for $\mathcal{R}$ scenario as the $\mathcal{H}$ case is
by default a source of HC condition, hence, would not make a big impact in
changing the patterns across the LC and HC conditions. Based on ANOVA results,
taking just the 5 AOI groups (head, arms, hands, torso, legs) for the robot in
both LC and HC conditions, the fixations on the head in the HC condition was
found to be significantly higher than that in the LC condition (F[1,36] = 4.55,
p < .05). For all other AOI groups, the fixations across LC and HC were almost
the same. Figure 3(b) shows the distribution of proportion of time spent gazing
on the 5 AOIs for LC and HC conditions.

@@

Based on the results that we obtained, we can now verify our four hypotheses.
For the first hypothesis where we state that the gaze patterns can distinguish
between $\mathcal{H}$ and $\mathcal{R}$ interaction scenarios, we get greater
amount of fixation on the head, arms and torso for the $\mathcal{H}$ scenario as
compared to the $\mathcal{R}$ scenario. This can be explained by the fact that
human is by default perceived as a high cognitive agent compared to a robot.
Hence, the proportion of time spent on looking at the head is more in case of
human videos as compared to robot videos. But the trend is opposite for legs.
This might be explained by the fact that the participants are fascinated by the
joints on the robot's legs \ie the novelty effect. Overall, this
result weakly validates our hypothesis.

In the second hypothesis, where we claim that $\delta_{\mathcal{H},\mathcal{R}}$
should correlate with the participants' ICA, we obtain in our results, a
significant negative correlation between the two quantities. From the negative
correlation, we can understand that if ICA is high, it means that the
\textit{human likeliness ascription} (HLA) is high (which means that there is a
greater tendency to anthropomorphize) which indicates that
$\delta_{\mathcal{H},\mathcal{R}}$ should be low. This supports our hypothesis
and can be explained by the fact that if HLA is high for a participant, then
even the $\mathcal{R}$ videos are quite human-like for such participant.

>>>>

To study this effect, we propose an original methodology based on eye-tracking
and a series of stimuli that are visually identical and yet elicit different
assumptions regarding the cognitive capabilities of the robot. We then correlate
the gaze patterns with established questionnaires that assess anthropomorphic
attributions.

@@

Anthropomorphism is seen as a special kind of social (human-like) engagement
with robots. We made an attempt to analyze anthropomorphism in a
\textit{human-robot} interaction by utilizing the gaze patterns of the
participants (who watched this interaction). These gaze patterns were compared
to the gaze patterns for a similar \textit{human-human} interaction setting. The
``human'' part of the human-robot and human-human interactions mentioned above
is only in the form of an audio command and not physically present in the scene.
Hence, we represent the interactions with robot($\mathcal{R}$) and human($\mathcal{H}$) in
this report for the human-robot and human-human settings respectively.

There were four hypotheses made in this experiment\fxwarning{need to change order of hypotheses(as Kshitij suggested) but the flow breaks by placing H4 first, H1 last}. We hypothesized
(\textbf{H1}) that the gaze patterns can distinguish between human and
robot interaction scenarios. Further, this gaze pattern difference can
be denoted as the distribution of gaze on areas of interest in the scene.
Secondly, we hypothesized (\textbf{H2}) that the difference in gaze patterns
between human and robot conditions
($\delta_{\mathcal{H},\mathcal{R}}$) correlate with the participants'
\textit{initial capital of anthropomorphism} (ICA), where the ICA was measured
as the sum of the ratings (responses) given by the participants to the questions
of the pre-questionnaire. This means that for participants whose ICA is low, the
gaze patterns should be significantly different for the robot videos
compared to the human videos.

@@

\fxwarning{This whole para already being discussed under Experimental Design. Can remove this para}We used stationary eye tracking technique for tracking the gaze patterns and
``Nao", a robot manufactured by Aldebaran Robotics was used in this
experiment. The
interactions were recorded as videos and were then shown to the participants.
The scenarios that were covered in the videos were aimed at eliciting the
human-like or high-cognitive (HC) feelings for the robot in one setting and
robot-like or low-cognitive (LC) feelings in the other setting. We tried to keep our distribution of
participants uniform across all variations of the scenarios to avoid any biases
to our results. The change in the feelings\fxwarning{can we have a more specific word than 'feeling'?} of participants were recorded in the
form of response to two questionnaires before and after the experiment. The
difference in the response of the two questionnaires was used to measure the
impact the videos had on the participants.

\fxwarning{This para is here just to justify why 3rd scenario isn't used. Else the contents already being discussed in sections 3.1, 3.2}As mentioned earlier, the human element in the robot interaction was in
the form of a command given by the human to the
robot. This command (\eg ``pick up the brown toy") was used to prime
the context thereby classifying the scenario as LC or HC. Initially we had three
different scenarios where the robot/human was asked:

@@

After filling the pre-questionnaire, participants watched the robot and
human interaction videos.

@@

Among the 10 AOIs, we grouped the AOIs corresponding to the actor into 4
categories : Head, Arm (containing both arms and hands), Torso, Leg(containing
both legs). And this is the result that we obtained from the ANOVA between gaze
patterns on the AOIs versus the human and robot videos :

\textit{\textbf{head}}: the fixations on the head for the human video
were observed to more than that for the robot video (F[1,36] = \ 6.60, p
< .05)

\textit{\textbf{arm}}\ : the fixations on the arms for the $\mathcal{H}$ video
were also greater than that for the robot video (F[1,36] = 18.65, p <
.01)

\textit{\textbf{leg}}\hspace{0.18cm} : the fixations on the legs were much lower
for the human video as compared to the robot video (F[1,36] = \
2.89, p < .1)

\textit{\textbf{torso}} : the fixations on the torso was more for the
human video than for the robot video (F[1,36] = \ 3.54, p < .1)

@@

This test was done only for robot scenario as the human case is
by default a source of HC condition, hence, would not make a big impact in
changing the patterns across the LC and HC conditions. Based on ANOVA results,
taking just the 5 AOI groups (head, arms, hands, torso, legs) for the robot in
both LC and HC conditions, the fixations on the head in the HC condition was
found to be significantly higher than that in the LC condition (F[1,36] = 4.55,
p < .05). For all other AOI groups, the fixations across LC and HC were almost
the same. Figure 3(b) shows the distribution of proportion of time spent gazing
on the 5 AOIs for LC and HC conditions.

@@

Based on the results that we obtained, we can now verify our four hypotheses.
For the first hypothesis where we state that the gaze patterns can distinguish
between human and robot interaction scenarios, we get greater
amount of fixation on the head, arms and torso for the human scenario as
compared to the robot scenario. This can be explained by the fact that
human is by default perceived as a high cognitive agent compared to a robot.
Hence, the proportion of time spent on looking at the head is more in case of
human videos as compared to robot videos. But the trend is opposite for legs.
This might be explained by the fact that the participants are fascinated by the
joints on the robot's legs \ie the novelty effect. Overall, this
result weakly validates our hypothesis.

In the second hypothesis, where we claim that $\delta_{\mathcal{H},\mathcal{R}}$
should correlate with the participants' ICA, we obtain in our results, a
significant negative correlation between the two quantities. From the negative
correlation, we can understand that if ICA is high, it means that the
\textit{human likeliness ascription} (HLA) is high (which means that there is a
greater tendency to anthropomorphize) which indicates that
$\delta_{\mathcal{H},\mathcal{R}}$ should be low. This supports our hypothesis
and can be explained by the fact that if HLA is high for a participant, then
even the robot videos are quite human-like for such participant.
